### 2015-07-07 narrative/qos.tex
another reference

More specifically, the coarseness of a search space partitioning limits the search time within 
a partition, i.e. finely partitioned search spaces require little or no search within a partition 
but offer little placement flexibility. Partitioning can also be fine in one dimension and coarse 
in another to allow flexibility where it is most needed while still ensuring fast finding. For 
example, a hash function can finely partition a low storage tier but each partition can extend 
across multiple tiers so that a search still has to occur in order to find a resource on a particular 
tier.

Specifically, we will address the following research questions:\\
  1) Can we make any guarantees in a scalable decentralized system?; \\
  2) What quality of service metrics can be make guarantees on in a scalable
    way?;\\
  3) What kind of error rates will we have in our estimation and what error
    rates are acceptable?;\\
  4) How much will the qos scheduler, admission control, manager cost in
    terms of resources and time?;\\
  5) How do we make the scheduler scalable with the size of the system?

\subsubsection{QoS}
\paragraph{Background:} Quality of Service (QoS) refers to the
properties of the performance quality of a particular service, in
this case the storage system.
%Performance quality can be expressed in either relative or absolute
%terms. Examples of relative performance terms are ``fair'',
%``proportional'', or ``priority/class-based'' (``the higher the
%priority the better the service'' or ``1st class is better than
%2nd''). The key advantage of relative performance terms is that
%they are easy to implement. The key disadvantage is the difficulty
%of making any guarantees based on those implementations --
%even relative guarantees are mired by the well-known effect of
%priority inversion~\cite{lampson:cacm80}. Examples of absolute
%performance terms are ``rate-based'', ``soft real-time'', and
%``hard real-time''. The key advantage of absolute performance
%terms are that they enable the implementation of strong
%guarantees: absolute terms enable agreements between application
%tasks and storage that we call \emph{reservations} and that do not
%change meaning depending
%on the storage system's workload. The key challenge of absolute
%performance terms is that their implementation is non-trivial,
%especially in large-scale systems.
One of the key differentiating features this project offers is driving storage
decisions through QoS \emph{reservations}, rather than continuing the current model
of allowing applications to compete freely without restriction, for part or all of the storage
resources. This traditional approach leads to interference effects
\cite{lofstead:2010:io-variability,liu_hotstorage} that can greatly impact IO performance predictability. 
%Further, with the introduction of additional tiers in the
%storage stack, the performance variability will increase with greater
%competiion for limited high performance resources. 
%% Temporaily commented out the above sentence, because it may not be true for the next DOE systems. 
Unfettered, this competition can yield a lower system and application performance 
than the case where applications attempt to reserve storage resources, thereby enabling the storage system
to reason over its performance in terms of reservations and actual
performance.
In the cases where an application arrives that needs to run more urgently
than any of the other already running applications, the system
can rapidly respond to it by reducing the amount of resources taken 
by less urgent applications, allowing the urgent application to finish,
and later reverting back to the previous committed resource level for the rest.
This can be automatically enforced via user- (or administrator-) specified \textit{policies}
(section \ref{}).

>>>>

More specifically, the coarseness of a search space partitioning limits the search time within 
a partition, i.e. finely partitioned search spaces require little or no search within a partition 
but offer little placement flexibility. Partitioning can also be fine in one dimension and coarse 
in another to allow flexibility where it is most needed while still ensuring fast finding. For 
example, a hash function can finely partition a low storage tier but each partition can extend 
across multiple tiers so that a search still has to occur in order to find a resource on a particular 
tier.  Specifically, we will address the following research questions:
\begin{itemize}
  \item Can we make any guarantees in a scalable decentralized system?; 
 \item  What quality of service metrics can be make guarantees on in a scalable
    way?;
  \item What kind of error rates will we have in our estimation and what error
    rates are acceptable?;
  \item How much will the qos scheduler, admission control, manager cost in
    terms of resources and time?;
  \item  How do we make the scheduler scalable with the size of the system?
\end{itemize}

\subsubsection{QoS}
\paragraph{Background:} Quality of Service (QoS) refers to the
properties of the performance quality of a particular service, in
this case the storage system.
%Performance quality can be expressed in either relative or absolute
%terms. Examples of relative performance terms are ``fair'',
%``proportional'', or ``priority/class-based'' (``the higher the
%priority the better the service'' or ``1st class is better than
%2nd''). The key advantage of relative performance terms is that
%they are easy to implement. The key disadvantage is the difficulty
%of making any guarantees based on those implementations --
%even relative guarantees are mired by the well-known effect of
%priority inversion~\cite{lampson:cacm80}. Examples of absolute
%performance terms are ``rate-based'', ``soft real-time'', and
%``hard real-time''. The key advantage of absolute performance
%terms are that they enable the implementation of strong
%guarantees: absolute terms enable agreements between application
%tasks and storage that we call \emph{reservations} and that do not
%change meaning depending
%on the storage system's workload. The key challenge of absolute
%performance terms is that their implementation is non-trivial,
%especially in large-scale systems.
One of the key differentiating features this project offers is driving storage
decisions through QoS \emph{reservations}, rather than continuing the current model
of allowing applications to compete freely without restriction, for part or all of the storage
resources. This traditional approach leads to interference effects
\cite{lofstead:2010:io-variability,liu_hotstorage} that can greatly impact IO performance predictability. 
%Further, with the introduction of additional tiers in the
%storage stack, the performance variability will increase with greater
%competiion for limited high performance resources. 
%% Temporaily commented out the above sentence, because it may not be true for the next DOE systems. 
Unfettered, this competition can yield a lower system and application performance 
than the case where applications attempt to reserve storage resources, thereby enabling the storage system
to reason over its performance in terms of reservations and actual
performance.
In the cases where an application arrives that needs to run more urgently
than any of the other already running applications, the system
can rapidly respond to it by reducing the amount of resources taken 
by less urgent applications, allowing the urgent application to finish,
and later reverting back to the previous committed resource level for the rest.
This can be automatically enforced via user- (or administrator-) specified \textit{policies}\S\ref{sec:data-description}.
